---
title: "Preprocessing Fitfiles"
author: "Matthew Hull"
date: "`r format(Sys.Date())`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.retina = 2)

```


```{r echo=F, message=FALSE, warning=FALSE}
library(XML)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(xts)
library(zoo)
library(spacetime)
library(lubridate)
library(RColorBrewer)
library(viridis)
library(mice)
library(reshape2)
require(gridExtra)
library(spatstat.utils)
library(latex2exp)
library(sqldf)

### LOAD 
df <- read.csv('data/fit.csv', header=TRUE, sep=",")
```


Distance from the fitfile was expressed in meters, converted to miles.  Time is converted from seconds to hours.  
```{r}
df$total_distance = df$total_distance * .000621
df$total_timer_time = round((df$total_timer_time / 60) / 60,2)
df['mph'] = round(df$total_distance / df$total_timer_time,1)
```

Original values from fitfile converted to the desired fields
TODO: make this into table. 
# timestamp = timestamp
# total_timer_time = duration
# total_distance = totalDistance
# total_calories = totalEnergyBurned
# source = sourceName.x
# avg_heart_rate = hr_value
# sport = workoutType

```{r echo=F}
# rename cols to match with apple export
colnames(df) <- c('timestamp', 'duration', 'totalDistance', 'totalEnergyBurned', 'sourceName.x', 'hr_value', 'workoutType', 'mph')

df['month'] <- lubridate::month(df$timestamp, label=T)
df['ymd'] <- NA
df['ymd'] <- lubridate::date(df$timestamp)
df['timestamp'] <- NULL


df$workoutType <- as.character(df$workoutType)
df$workoutType[df$workoutType=="fitness_equipment"] = "elliptical"
df$workoutType[df$workoutType=="generic"] = "other"
df$workoutType <- as.factor(df$workoutType)

df <- subset(df, df$workoutType != "other")
```


```{r}
ggplot(df, mapping=aes(duration)) + 
  geom_density() + 
  geom_vline(data=df, aes(xintercept = mean(df$duration))
           , color="purple"
           , size=0.75
           , alpha=0.60
           , lty="dashed") +  
  facet_wrap(~month) +
  ggtitle("Workout Duration by Month")

```

```{r}
p <- ggplot(df[df$month=="Feb",], aes(duration)) + 
  geom_density() +
  theme_void()
library(svglite)
ggsave(file="~/Desktop/feb.svg", plot=p, width=10, height=8)
```

```{r}
df_2016 <- subset(df, format(as.Date(df$ymd),"%Y")==2016)
df_2017 <- subset(df, format(as.Date(df$ymd),"%Y")==2017)
df_2018 <- subset(df, format(as.Date(df$ymd),"%Y")==2018)
df_2019 <- subset(df, format(as.Date(df$ymd),"%Y")==2019)
```

```{r}
ggplot(df_2016, mapping=aes(duration)) + 
  geom_density() + 
  facet_wrap(~month) +
  ggtitle("2016 Workouts Duration by Month")
```


```{r}
ggplot(df_2017, mapping=aes(duration)) + 
  geom_density() + 
  facet_wrap(~month) +
  ggtitle("2017 Workouts Duration by Month")
```

```{r}
ggplot(df_2018, mapping=aes(duration)) + 
  geom_density() + 
  facet_wrap(~month) +
  ggtitle("2018 Workouts Duration by Month")
```


```{r}
ggplot(df_2019, mapping=aes(duration)) + 
  geom_density() + 
  facet_wrap(~month) +
  ggtitle("2019 Workouts Duration by Month")
```

```{r}
ggplot(df, aes(workoutType)) +
  geom_bar(aes(fill=workoutType))
```

